Robust Trajectory Optimization on a Quantum System

### 2021-01-26 paper/a1longitude.tex
revised based on dave comments

\begin{table}[ht]
  \begin{tabular}{c | c | c | c | c | c | c}
         & $P_{1\textrm{A}}$ & $P_{1\textrm{N}}$ & & GE$_{\textrm{A}}$ & GE$_{\textrm{N}}$ &\\
    Gate & $(10^{-5})$ & $(10^{-5})$ & $P_{1\textrm{A}}/ P_{1\textrm{N}}$ & $(10^{-5})$ &
    $(10^{-5})$ & GE$_{\textrm{A}} / \textrm{GE}_{\textrm{N}}$\\
    \hline
    Z/2 & 5.745 & 1.149 & 5.000 & 1.776 & 0.371 & 4.787\\
    Y/2 & 5.253 & 1.157 & 4.540 & 1.539 & 0.370 & 4.159\\
    X/2 & 16.251 & 2.660 & 6.109 & 5.347 & 0.863 & 6.196\\
  \end{tabular}
  \caption{
    Single gate depolarization probability (P) ratios
    and single gate error due to depolarization (GE) ratios.
    Values are reported for the analytic (A) and numerical (N) techniques.
  }
  \label{tab:longitude}
\end{table}

To compute the gate error due to depolarization
we employ the Lindblad master equation. This equation takes the form:
\begin{equation}
  \frac{d}{dt} \rho = \frac{-i}{\hbar} [H, \rho]
  + \sum_{i = 1}^{n^{2} - 1} \gamma_{i} (L_{i} \rho L_{i}^{\dagger}
  - \frac{1}{2} \{L_{i}^{\dagger} L_{i}, \rho\})
\end{equation}
where $\rho = \ket{\psi}\bra{\psi}$ is the density matrix, $n$ is the
dimension of the Hilbert space,
$[\cdot, \cdot]$ is the algebraic commutator, and $\{\cdot, \cdot \}$ is the algebraic
anti-commutator.
For depolarization $\gamma_{\uparrow} = T_{1, \uparrow}^{-1}$,
$\gamma_{\downarrow} = T_{1, \downarrow}^{-1}$,
$L_{\uparrow} = \sigma^{+}/2$, and
$L_{\downarrow} = \sigma^{-}/2$ where $\sigma^{\pm} = \sigma_{x} \pm i \sigma_{y}$.
Both $T_{1, \uparrow}$ and $T_{1, \downarrow}$ are obtained from the spline
shown in Figure \ref{fig:longitudeb}.
We obtain the $T_{1}$ values in this spline
by driving the qubit at the desired flux amplitude
and monitoring the resultant decay.
For more details consult \cite{zhang2020universal}.

Exponential integrators can be employed to integrate the Lindblad master equation
using the Vectorization/Choi-Jamiolkowski isomorphism \cite{Landi2018},
\begin{equation}
  \frac{d}{dt} \textrm{vec}({\rho}) = \hat{\mathcal{L}} \textrm{vec}({\rho})
\end{equation}
\begin{equation}
  \begin{aligned}
    \hat{\mathcal{L}} &= -i(I \otimes H - H^{T} \otimes I)\\
    &+ \sum_{i = 1}^{n^{2} - 1} \gamma_{i}
    (L_{i}^{*} \otimes L_{i} - \frac{1}{2} (I \otimes L_{i}^{\dagger}L_{i}
    - L_{i}^{T}L_{i}^{*} \otimes I))
  \end{aligned}
\end{equation}
where $\rho = \sum_{i, j} \alpha_{i, j} \ket{i}\bra{j}$
and $\textrm{vec}(\rho) = \sum_{i, j} \alpha_{i, j} \ket{i} \otimes \ket{j}$.
We use zero-order hold on the controls so the exact solution is
$\textrm{vec}(\rho_{k + 1}) = \exp(\Delta t_{k} \hat{\mathcal{L}}_{k}) \textrm{vec}(\rho_{k})$.
This isomorphism transforms $(n^{2} \times n^{2}) \times (n^{2} \times n^{2})$
matrix-matrix multiplications to $(n^{4} \times n^{4}) \times n^{4}$ matrix-vector
multiplications. For small $n$ and zero-order hold on the controls, we find that it is
faster to use an exponential integrator on the vectorized equation than to perform
Runge-Kutta on the unvectorized equation. The latter requires decreasing the integration
time step to maintain accuracy, resulting in more knot points.

>>>>

\begin{table}[ht]
  \begin{tabular}{c | c | c | c | c | c | c}
         & $P_{1\textrm{A}}$ & $P_{1\textrm{N}}$ & & GE$_{\textrm{A}}$ & GE$_{\textrm{N}}$ &\\
    Gate & $(10^{-5})$ & $(10^{-5})$ & $P_{1\textrm{A}}/ P_{1\textrm{N}}$ & $(10^{-5})$ &
    $(10^{-5})$ & GE$_{\textrm{A}} / \textrm{GE}_{\textrm{N}}$\\
    \hline
    Z/2 & 5.745 & 1.149 & 5.000 & 1.776 & 0.371 & 4.787\\
    Y/2 & 5.253 & 1.157 & 4.540 & 1.539 & 0.370 & 4.159\\
    X/2 & 16.251 & 2.660 & 6.109 & 5.347 & 0.863 & 6.196\\
  \end{tabular}
  \caption{
    Single gate depolarization probability (P)
    and single gate error due to depolarization (GE).
    Values are reported for the analytic (A) and numerical (N) gates.
  }
  \label{tab:longitude}
\end{table}

We employ the Lindblad master equation
to compute the gate error due to depolarization.
This equation takes the form:
\begin{equation}
  \frac{d}{dt} \rho = \frac{-i}{\hbar} [H, \rho]
  + \sum_{i = 1}^{n^{2} - 1} \gamma_{i} (L_{i} \rho L_{i}^{\dagger}
  - \frac{1}{2} \{L_{i}^{\dagger} L_{i}, \rho\}),
\end{equation}
where $\rho = \ket{\psi}\bra{\psi}$ is the density matrix, $n$ is the
dimension of the Hilbert space,
$[\cdot, \cdot]$ is the algebraic commutator, and $\{\cdot, \cdot \}$ is the algebraic
anti-commutator.
For depolarization $\gamma_{\uparrow} = T_{1, \uparrow}^{-1}$,
$\gamma_{\downarrow} = T_{1, \downarrow}^{-1}$,
$L_{\uparrow} = \sigma^{+}/2$, and
$L_{\downarrow} = \sigma^{-}/2$ where $\sigma^{\pm} = \sigma_{x} \pm i \sigma_{y}$.
Both $T_{1, \uparrow}$ and $T_{1, \downarrow}$ are obtained from the spline
shown in Figure \ref{fig:longitudeb}.
We obtain the $T_{1}$ values in this spline
by driving the qubit at the desired flux amplitude
and monitoring the resultant decay. For more details
on these measurements, consult \cite{zhang2020universal}.

So that we may use exponential integrators, we employ
the Vectorization/Choi-Jamiolkowski isomorphism \cite{Landi2018},
\begin{equation}
  \frac{d}{dt} \textrm{vec}({\rho}) = \hat{\mathcal{L}} \textrm{vec}({\rho}),
\end{equation}
\begin{equation}
  \begin{aligned}
    \hat{\mathcal{L}} &= -i(I \otimes H - H^{T} \otimes I)\\
    &+ \sum_{i = 1}^{n^{2} - 1} \gamma_{i}
    (L_{i}^{*} \otimes L_{i} - \frac{1}{2} (I \otimes L_{i}^{\dagger}L_{i}
    - L_{i}^{T}L_{i}^{*} \otimes I)),
  \end{aligned}
\end{equation}
where $\rho = \sum_{i, j} \alpha_{i, j} \ket{i}\bra{j}$
and $\textrm{vec}(\rho) = \sum_{i, j} \alpha_{i, j} \ket{i} \otimes \ket{j}$.
We use zero-order hold on the controls so the exact solution is
$\textrm{vec}(\rho_{k + 1}) = {\exp}{\textstyle(}\Delta t_{k} \hat{\mathcal{L}}_{k}{\textstyle)} \textrm{vec}(\rho_{k})$.
This isomorphism transforms $(n^{2} \times n^{2}) \times (n^{2} \times n^{2})$
matrix-matrix multiplications to $(n^{4} \times n^{4}) \times n^{4}$ matrix-vector
multiplications. For small $n$ and zero-order hold on the controls, we find that it is
faster to use an exponential integrator on the vectorized equation than to perform
Runge-Kutta on the unvectorized equation. The latter requires decreasing the integration
time step to maintain accuracy, resulting in more knot points.

### 2021-01-26 paper/a2unscented.tex
revised based on dave comments

\section{Unscented Transformation}
\label{appendix:unscented}
In this section, we outline the full unscented sampling procedure.
We consider a state $\psi \in \mathbb{R}^{2n}$ with
a deviant parameter $\lambda \in \mathbb{R}^{d}$ and dynamics
$\psi_{k + 1} = f(\psi_{k}, \lambda_{k})$.
The nominal initial state is given by $\psi_{0}$ with an associated
positive-definite covariance matrix $P_{0} \in \mathbb{R}_{++}^{2n \times 2n}$
which describes the uncertainty in the initial state.
$P_{0}$ is typically non-zero even if the state preparation error is negligible.
The deviant parameter
has zero-mean and its distribution is given by the covariance matrix
$L_{k} \in \mathbb{R}_{++}^{d \times d}$ at knot point $k$. The zero mean assumption
is convenient for deriving the update procedure. A non-zero mean can be encoded
in the dynamics.

The initial $4n + 2d$ sigma points and initial $4n + 2d$ deviant parameters are sampled
from the initial distributions,
\begin{equation}\label{eq:uupdate}
  \begin{bmatrix} \Psi_{0}^{i} \\ \Lambda_{0}^{i} \end{bmatrix} =
  \begin{bmatrix} \bar{\Psi}_{0} \\ 0\end{bmatrix}
    \pm \beta \sqrt{\begin{bmatrix} P_{0} & 0\\ 0 & L_{0}\end{bmatrix}}^{\; i}
\end{equation}
We have written $\bar{\Psi}_{0} = \psi_{0}$. $\beta$
is a hyperparameter which controls the spacing of the covariance contour.
The $(\pm)$ is understood to take $(+)$ for $ i \in \{1, \dots, 2n + d\}$ and $(-)$ for
$i \in \{2n + d + 1, \dots, 4n + 2d\}$. We use the Cholesky factorization
to compute the square root of the
joint covariance matrix, though other methods
such as the principal square root may be employed.
The superscript on the matrix square root indicates the $i$\textsuperscript{th}
column (mod $2n + d$) of the lower triangular Cholesky factor.
Then, the sigma points are normalized,
\begin{equation}\label{eq:unormalize}
  \Psi_{0}^{i} \gets \frac{\Psi_{0}^{i}}{\sqrt{\Psi_{0}^{i^{T}} \Psi_{0}^{i}}}
\end{equation}
The sigma points are propagated to the next knot point,
\begin{equation}\label{eq:upropagate}
  \Psi_{1} = f(\Psi_{0}, \Lambda_{0})
\end{equation}
The mean and covariance of the sigma points are computed,
\begin{align}
  \bar{\Psi}_{1} &= \frac{1}{4n + 2d} \sum_{i = 1}^{4n + 2d} \Psi_{1}^{i}\\
  P_{1} &= \frac{1}{2 \beta^{2}} \sum_{i = 1}^{4n + 2d}
  (\Psi^{i}_{1} - \bar{\Psi}_{1})^{T}(\Psi^{i}_{1} - \bar{\Psi}_{1})
\end{align}
The sigma points are then resampled and propagated to the next knot point using
\eqref{eq:uupdate}, \eqref{eq:unormalize}, and \eqref{eq:upropagate}. Our
choice of sigma points follows the prescription in equation 11 of \cite{julier2004unscented}.
Prescriptions that require fewer sigma points exist \cite{julier2002reduced}.

>>>>

\section{Unscented Transformation}
\label{appendix:unscented}
In this section, we outline the full unscented sampling procedure.
In the unscented sampling method, we consider a state $\psi \in \mathbb{R}^{2n}$, 
an uncertain parameter $\lambda \in \mathbb{R}^{d}$, and discrete dynamics
$\psi_{k + 1} = f(\psi_{k}, \lambda_{k})$.
The state is obtained with an isomorphism \eqref{eq:isomorphism} and
we omit bra-ket notation to emphasize that the state is real.
The nominal initial state is given by $\bar{\psi}_{1}$ with an associated
positive-definite covariance matrix $P_{1} \in \mathbb{S}_{++}^{2n}$
which describes the uncertainty in the initial state.
$P_{1}$ is typically non-zero even if the state preparation error is negligible.
The uncertain parameter has zero-mean
and its distribution is given by the covariance matrix
$L_{k} \in \mathbb{S}_{++}^{d}$ at knot point $k$. The zero-mean assumption
is convenient for deriving the update procedure. A non-zero mean can be encoded
in the discrete dynamics function $f(\psi_{k}, \lambda_{k})$.

The initial $4n + 2d$ sample states and initial $4n + 2d$
uncertain parameters are sampled from the initial distributions,
\begin{equation}\label{eq:uupdate}
  \begin{bmatrix} \psi_{1}^{j} \\ \lambda_{1}^{j} \end{bmatrix} =
  \begin{bmatrix} \bar{\psi}_{1} \\ 0\end{bmatrix}
    \pm \beta \sqrt{\begin{bmatrix} P_{1} & 0\\ 0 & L_{1}\end{bmatrix}}^{\; j}.
\end{equation}
$\beta$ is a hyperparameter that controls the spacing of the covariance contour.
The $(\pm)$ is understood to take $(+)$ for $j \in \{1, \dots, 2n + d\}$ and $(-)$ for
$j \in \{2n + d + 1, \dots, 4n + 2d\}$. We use the Cholesky factorization
to compute the square root of the
joint covariance matrix, though other methods
such as the principal square root may be employed.
The superscript on the matrix square root indicates the $i$\textsuperscript{th}
column (mod $2n + d$) of the lower triangular Cholesky factor.
Then, the sample states are normalized,
\begin{equation}\label{eq:unormalize}
  \psi_{1}^{j} \rightarrow \frac{\psi_{1}^{j}}{\sqrt{{\psi_{1}^{j}}^{T} \psi_{1}^{j}}}.
\end{equation}
The sample states are propagated to the next knot point,
\begin{equation}\label{eq:upropagate}
  \psi^{j}_{2} = f(\psi^{j}_{1}, \lambda^{j}_{1}).
\end{equation}
The mean and covariance of the sample states are computed,
\begin{align}
  \bar{\psi}_{2} &= \frac{1}{4n + 2d} \sum_{j = 1}^{4n + 2d} \psi_{2}^{j},\\
  P_{2} &= \frac{1}{2 \beta^{2}} \sum_{j = 1}^{4n + 2d}
  (\psi^{j}_{2} - \bar{\psi}_{2})(\psi^{j}_{2} - \bar{\psi}_{2})^{T}.
\end{align}
The sample states are then resampled and propagated to the next knot point using
\eqref{eq:uupdate}, \eqref{eq:unormalize}, and \eqref{eq:upropagate}. Our
choice of sample states (sigma points) follows equation 11 of
\cite{julier2004unscented}.
Prescriptions that require fewer sigma points exist \cite{julier2002reduced}.

### 2021-01-26 paper/a3derivative.tex
majority of jens and colm comments adressed
revised based on dave comments

\section{Derivative Method \label{appendix:derivative}}
We comment on the optimization metrics of the derivative methods and then
outline how to efficiently integrate their dynamics.
The 1\textsuperscript{st}-order derivative method tends
to outperform the 2\textsuperscript{nd}-order
derivative method in the small, static detuning regime, see Figure \ref{fig:staticb}.
The norms of the state derivatives for the 1\textsuperscript{st}- and 2\textsuperscript{nd}-order
methods are provided in Table \ref{tab:dnorm} for the solutions to
the numerical experiment detailed in Section \ref{sec:static} at $t_{N} = 60$ns.
The 2\textsuperscript{nd}-order method is able to decrease the 2\textsuperscript{nd}-order
state derivate norm relative to the 1\textsuperscript{st}-order method at the expense of increasing
its 1\textsuperscript{st}-order derivative norm. In the problem
we have studied it is likely the 2\textsuperscript{nd}-order derivative norm has a smaller
contribution to the gate error than the 1\textsuperscript{st}-order derivative norm. A
careful analysis of contributions at each order could be used to predict the efficacy of the
derivative method for future problems.

\begin{table}[ht]
  \begin{tabular}{c | c | c}
    Method & $\norm{\partial_{f_{q}} \psi_{N}}_{2}$ ($10^{3}$)
    & $\norm*{\partial^{2}_{f_{q}} \psi_{N}}_{2}$ ($10^{6}$)\\
    \hline
    D1 & 0.436 & 57.817\\
    D2 & 1.702 & 9.030\\
  \end{tabular}
  \caption{Norm of state derivates with respect to the qubit frequency
    for $Z/2$ gates optimized using the derivative methods. The norms are computed
    at the end of the gate $t_{N} = 60$ns
    and are averaged over the four state derivatives.}
  \label{tab:dnorm}
\end{table}

The dynamics for the derivative methods can be integrated efficiently using exponential integrators
\cite{auer2018magnus, berland2005solving, einkemmer2017performance}.
General exponential integrators break the dynamics into a linear term and a non-linear term.
For example, the dynamics of the first state derivative in
units of $i\hbar = 1$ are $\frac{d}{dt} \ket{\partial_{\lambda} \psi} =
H \ket{\partial_{\lambda} \psi} + (\partial_{\lambda} H) \ket{\psi}$.
The linear term is $L = H$ and the non-linear term is $N = (\partial_{\lambda} H) \ket{\psi}$.
With zero-order hold on the controls the exact solution is:
\begin{equation}
  \label{eq:dgeneralexp}
  \begin{aligned}
    \ket{\partial_{\lambda} \psi_{k + 1}} &= \exp(\Delta t_{k} L_{k})
    \ket{\partial_{\lambda} \psi_{k}}\\
    &+ \int_{0}^{\Delta t_{k}} \exp((\Delta t_{k} - t^{'})L_{k})
    N(t_{k} + t^{'}) dt^{'}\\
  \end{aligned}
\end{equation}
General exponential integrators proceed by breaking the integral in \eqref{eq:dgeneralexp}
into a discrete sum, similar to the procedure
for Runge-Kutta schemes. We use a simple approximation known as the Lawson-Euler
method \cite{berland2005solving},
\begin{equation}
  \begin{aligned}
    \ket{\partial_{\lambda} \psi_{k + 1}} &\approx \exp(\Delta t_{k}L_{k}) \ket{\partial_{\lambda} \psi_{k}}\\
    &+ \exp(\Delta t_{k}L_{k}) N_{k}\\
  \end{aligned}
\end{equation}
This method provides a good tradeoff between accuracy and efficiency, requiring one unique matrix
exponential computation per stage. Integration accuracy is not of the utmost importance because the
state derivatives guide the optimization, and do not correspond to experimental parameters
which must be realized with high accuracy.

>>>>

\section{Derivative Method \label{appendix:derivative}}
Here, we outline how to efficiently integrate the dynamics
of the derivative method using exponential integrators.
General exponential integrators break the dynamics into a linear term and a non-linear term.
For example, the dynamics of the first state derivative in
units of $i\hbar = 1$ are $\frac{d}{dt} \ket{\partial_{\lambda} \psi} =
H \ket{\partial_{\lambda} \psi} + (\partial_{\lambda} H) \ket{\psi}$.
The linear term is $L = H$ and the non-linear term is $N = (\partial_{\lambda} H) \ket{\psi}$.
With zero-order hold on the controls the exact solution is:
\begin{equation}
  \label{eq:dgeneralexp}
  \begin{aligned}
    \ket{\partial_{\lambda} \psi_{k + 1}} &= \exp(\Delta t_{k} L_{k})
    \ket{\partial_{\lambda} \psi_{k}}\\
    &+ \int_{0}^{\Delta t_{k}} \exp((\Delta t_{k} - t^{'})L_{k})
    N(t_{k} + t^{'}) dt^{'}.\\
  \end{aligned}
\end{equation}
General exponential integrators proceed by breaking the integral in \eqref{eq:dgeneralexp}
into a discrete sum, similar to the procedure
for Runge-Kutta schemes. We use a simple approximation known as the Lawson-Euler
method \cite{berland2005solving},
\begin{equation}
  \begin{aligned}
    \ket{\partial_{\lambda} \psi_{k + 1}} &\approx \exp(\Delta t_{k}L_{k}) \ket{\partial_{\lambda} \psi_{k}}\\
    &+ \exp(\Delta t_{k}L_{k}) N_{k} \Delta t_{k}.\\
  \end{aligned}
\end{equation}
This method provides a good tradeoff between accuracy and efficiency, requiring one unique matrix
exponential computation per stage. Integration accuracy is not of the utmost importance because the
state derivatives guide the optimization, and do not correspond to experimental parameters
which must be realized with high accuracy.

### 2021-01-26 paper/a4time.tex
majority of jens and colm comments adressed
revised based on dave comments

\section{Computational Performance \label{appendix:time}}
We provide runtimes for our optimizations and comment on the scaling of the
robustness methods. The runtimes for
the base optimization in Section \ref{sec:fluxonium},
the longitudinally aware optimization in Section \ref{sec:longitude},
and the robust optimizations in Section \ref{sec:static}
are presented in Table \ref{tab:time}
for a $Z/2$ gate at multiples of the analytic $Z/2$ gate time.
Compiler optimizations for statically-sized arrays were utilized
for all methods except for the unscented sampling method.
The unscented sampling method's augmented state vector size
was too large to take advantage of these optimizations,
adversely affecting its run time.
For the robust methods, the runtime scales super-linearly with the
gate time. We expect the runtime to scale linearly with the gate time
for large gate times because
the number of knot points scales linearly with the gate time.
We observe this behavior for the base method, which has a smaller
augmented state vector size than the robust methods.
We performed optimizations on a single CPU thread in this work as a proof
of concept. Future work will parallelize the robustness
methods across the initial states in the operator basis and utilize GPUs
\cite{leung2017speedup},
allowing for fast optimization on large Hilbert spaces.
\vspace*{\intextsep}

\begin{table}[H]
  \begin{tabular} {c | c | c | c | c | c | c}
    & \multicolumn{6}{c}{Wall Time ($\pm 0.001$ s)}\\
    \hline
    $t_{N}$ (ns) & Base & Long. & S & SU & D1 & D2\\
    \hline
    $18$ & 0.155 & 1.688 & 1.773 & 210.573 & 16.713 & 48.398\\ % 0.155049
    $36$ & 7.014 & - & 48.213 & 4566.236 & 67.838 & 81.030\\
    $72$ & 15.906 & - & 281.372 & 16575.308 & 266.997 & 332.182\\
  \end{tabular}
  \caption{
    Runtimes for $Z/2$ optimizations.
    Programs were executed on a single thread of an
    AMD Ryzen Threadripper 3970X 32-Core Processor.
  }
  \label{tab:time}
\end{table}

Now we present the problem size complexities for the robustness methods.
For the sampling method, the size of the augmented state vector
is $O(dn^{3})$, where $d$ is the number of deviant parameters and
$n$ is the dimension of the Hilbert space. There are $n^{2}$ initial states
in the operator basis, $2d$ sample states per initial state,
and each state has $2n$ real numbers.
For the unscented sampling method, the size of the augmented state vector
is $O(dn^{3} + n^{4})$.
There are $n^{2}$ initial states in the operator basis,
$2(2n + d)$ sample states per initial state,
and each state has $2n$ real numbers.
For the $m$\textsuperscript{th}-order derivative method, the size of the augmented state vector
is $O(dmn^{3})$. There are $n^{2}$
initial states in the operator basis, $dm$ state derivatives per initial state,
and each state has $2n$ real numbers.

>>>>

\section{Computational Performance \label{appendix:time}}
We provide runtimes for our optimizations and comment on the scaling of the
robustness methods. The runtimes for
the base optimization in Section \ref{sec:fluxonium},
the depolarization optimization in Section \ref{sec:longitude},
and the robust optimizations in Section \ref{sec:static}
are presented in Table \ref{tab:time}
for a $Z/2$ gate at gate times which are multiples of $1/4f_{q} \sim 18$ns.
We performed optimizations on a single core of
an AMD Ryzen Threadripper 3970X 32-Core Processor.
Future work will parallelize the robustness methods using GPUs
\cite{leung2017speedup},
which will enable fast optimizations on high-dimensional Hilbert spaces.

\begin{table}[H]
  \centering
  \begin{tabular} {c | c | c | c }
    & \multicolumn{3}{c}{Average Runtime (s)}\\
    \hline
    $t_{N}$ (ns) & $18$ & $36$ & $72$\\
    \hline
    Base & $0.155 \pm 0.008$ & $7.0 \pm 0.4$ & $15.9 \pm 0.8$\\
    Depol. & $1.69 \pm 0.08$ & - & -\\
    S & $1.77 \pm 0.09$ & $48 \pm 2$ & $280 \pm 10$\\
    U & $75 \pm 4$ & $340 \pm 20$ & $400 \pm 20$\\
    D1 & $6.1 \pm 0.3$ & $27 \pm 1$ & $65 \pm 3$\\
    D2 & $15.7 \pm 0.8$ & $17.3 \pm 0.9$ & $54 \pm 3$\\
  \end{tabular}
  \caption{
    Average runtimes for $Z/2$ optimizations
    using the base, depolarization, sampling (S),
    unscented Sampling (U), and the 1\textsuperscript{st}-
    and 2\textsuperscript{nd}-order derivative methods (D1, D2).
  }
  \label{tab:time}
\end{table}

Now we present the problem size complexities for the robustness methods.
For the sampling method, the size of the augmented state vector
is $O(dn^{3})$, where $d$ is the number of uncertain parameters and
$n$ is the dimension of the Hilbert space. There are $n^{2}$ initial states
in the operator basis, $2d$ sample states per initial state,
and each state has $2n$ real numbers.
For the unscented sampling method, the size of the augmented state vector
is $O(dn^{3} + n^{4})$.
There are $n^{2}$ initial states in the operator basis,
$2(2n + d)$ sample states per initial state,
and each state has $2n$ real numbers.
For the $m$\textsuperscript{th}-order derivative method, the size of the augmented state vector
is $O(dmn^{3})$. There are $n^{2}$
initial states in the operator basis, $dm$ state derivatives per initial state,
and each state has $2n$ real numbers.
